A highly-available move operation for replicated trees

### 2020-05-04 paper/move-op.tex
Add new references

This approach to determining ordering also easily supports reordering of child nodes within a parent: to move a node to a different position in a list, we use the list CRDT to generate a new ID at the desired position in the sequence.
Then we perform a move operation in which the parent node is unchanged, but the metadata is changed to this new ID.

@@

>>>>

This approach to determining ordering also easily supports reordering of child nodes within a parent: to move a node to a different position in a list, we use the list CRDT to generate a new ID at the desired position in the sequence~\cite{Kleppmann:2020jw}.
Then we perform a move operation in which the parent node is unchanged, but the metadata is changed to this new ID.

@@

After we performed the experiments described in Section~\ref{sec:move-is-hard}, the Dropbox engineering team published a blog post~\cite{Dropbox2020sync} acknowledging the problems of cycles and duplication due to concurrent moves.
